---
title: "quiz_4"
author: "Jordan Ho"
date: '2016-11-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)
library(haven)
library(cocor)

```

# Hypotheses

H1: There will be a positive relation between self-esteem and academic performance, such that as self-esteem increases, academic performance increases.

H2: There will be a negative relation between self-esteem and quality of dating relationships, such that as self-esteem increases, quality of dating relationships decreases.

H3: There will be a positive relation between self-esteem and quality of friendships, such that as self-esteem increases, quality of friendships increases.

# Analysis Plan A

H1: I will analyse my hypothesis using a bivariate correlation between self-esteem and academic performance. I will use a traditional power analyis since the population correlation is known (.50). I will require n = 28 in order to obtain power = .8

H2: I will analyse my hypothesis using a bivariate correlation between self-esteem and quality of dating relationships. I will use a safeguard power analysis because an estimate of the correlation exists (r=-.30). After using a lower-bound estimate for the population correlation, I will require n = 32

H3: I will analyse my hypothesis using a bivariate correlation between self-esteem and quality of friendships. Since no estimate of the correlation exists, I assume a small effect size (.07), which I will use in a power analysis. I will require n = 1598

The overall N I will use when conducting the study is N = 1658

# Analysis Plan B

H1: I will analyse my hypothesis using a bivariate correlation between self-esteem and academic performance. I will calculate sample size estimation. I will require an n = 38

H2: I will analyse my hypothesis using a bivariate correlation between self-esteem and quality of dating relationships. I will use a safeguard power analysis because the population correlation is not known, but an estimate of the correlation exists. I found that after a sample size analysis, n = 1235 produces a CI width (0.110216) that does not exceed the lower bound of the effect size estimate (r=-.1100677).

H3: I will analyse my hypothesis using a bivariate correlation between self-esteem and quality of friendships. Since no estimate of the correlation exists, I assume a small effect size (.07), which I will use in a power analysis and use the lower bound estimate in a sample size analysis. I will require n = 3100

The overall N I will use when conducting the study is N = 4373
